% do not change these two lines (this is a hard requirement
% there is one exception: you might replace oneside by twoside in case you deliver 
% the printed version in the accordant format
\documentclass[11pt,titlepage,oneside,openany]{book}
\usepackage{times}


\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{ntheorem}

% \usepackage{paralist}
\usepackage{tabularx}

% this packaes are useful for nice algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

%this package adds " " after commands, allows us a nicer
%formatting of texts
\usepackage{xspace}
\usepackage[colorlinks = false, pdfborder={0 0 0}]{hyperref}

% well, when your work is concerned with definitions, proposition and so on, we suggest this
% feel free to add Corrolary, Theorem or whatever you need
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}


% its always useful to have some shortcuts (some are specific for algorithms
% if you do not like your formating you can change it here (instead of scanning through the whole text)
\renewcommand{\algorithmiccomment}[1]{\ensuremath{\rhd} \textit{#1}}
\def\MYCALL#1#2{{\small\textsc{#1}}(\textup{#2})}
\def\MYSET#1{\scshape{#1}}
\def\MYAND{\textbf{ and }}
\def\MYOR{\textbf{ or }}
\def\MYNOT{\textbf{ not }}
\def\MYTHROW{\textbf{ throw }}
\def\MYBREAK{\textbf{break }}
\def\MYEXCEPT#1{\scshape{#1}}
\def\MYTO{\textbf{ to }}
\def\MYNIL{\textsc{Nil}}
\def\MYUNKNOWN{ unknown }
% simple stuff (not all of this is used in this examples thesis
\def\INT{{\mathcal I}} % interpretation
\def\ONT{{\mathcal O}} % ontology
\def\SEM{{\mathcal S}} % alignment semantic
\def\ALI{{\mathcal A}} % alignment
\def\USE{{\mathcal U}} % set of unsatisfiable entities
\def\CON{{\mathcal C}} % conflict set
\def\DIA{\Delta} % diagnosis
% mups and mips
\def\MUP{{\mathcal M}} % ontology
\def\MIP{{\mathcal M}} % ontology
% distributed and local entities
\newcommand{\cc}[2]{\mathit{#1}\hspace{-1pt} \# \hspace{-1pt} \mathit{#2}}
\newcommand{\cx}[1]{\mathit{#1}}
% complex stuff
\def\MER#1#2#3#4{#1 \cup_{#3}^{#2} #4} % merged ontology
\def\MUPALL#1#2#3#4#5{\textit{MUPS}_{#1}\left(#2, #3, #4, #5\right)} % the set of all mups for some concept
\def\MIPALL#1#2{\textit{MIPS}_{#1}\left(#2\right)} % the set of all mips


\begin{document}

\pagenumbering{roman}
% lets go for the title page, something like this should be okay
\begin{titlepage}
	\vspace*{2cm}
  \begin{center}
   {\Large Extraction of Goals from Premier League Match Reports using Natural Language Processing Techniques\\}
   \vspace{2cm} 
   {Student  Project\\}
   \vspace{2cm}
   {presented by\\
    Jochen H\"{u}l\ss \xspace  \&  Matthias Rabus \\
    Matriculation Number 1376749 \& 1207834 \\
   }
   \vspace{1cm} 
   {submitted to the\\
    Chair of Information Systems V\\
    Prof.\ Dr.\ Christian\ Bizer\\
    University Mannheim\\} \vspace{2cm}
   {Mai 2013}
  \end{center}
\end{titlepage} 

% no lets make some add some table of contents
\tableofcontents
\newpage

%\listofalgorithms

%\listoffigures

%\listoftables

% evntuelly you might add something like this
% \listtheorems{definition}
% \listtheorems{proposition}

\newpage


% okay, start new numbering ... here is where it really starts
\pagenumbering{arabic}

\chapter{Project Summary}
\section{Application Domain and Goals}

Due to the explosion of available textual data, text mining and Information Ex-
traction (IE) from texts have become important topics of study in recent years.
In particular, detection of relations between named entities is a challenging task
to automatically discover new relationships in texts.

Some previous works use hand-
crafted linguistic IE rules for that task which is time consuming [7,5]. Other
methods based on Machine Learning (ML) techniques [10] give good results but
run as a “black box”

Sequential pattern mining [1] is a data mining technique that aims at discovering
correlations between events through their order of appearance. Sequential pat-
tern mining is an important ﬁeld of data mining with broad applications (e.g.,
biology, marketing, security)

The project originates from a classical text mining problem. Generally speaking, we would like to deal with the question whether or not Natural Language Processing (NLP) tools are able to extract and correctly classify certain events in a given text. More specifically, our intention is machine-reading written reports on Premier League football matches. The particular event we are looking into is the scoring of a goal. At first sight, this appears rather straightforward, but by taking into account that there are numerous or even infinite ways to express that a team marks a goal, the difficulty to find as many of them as possible is challenging. Thus, a classification of text snippets based on manually found patterns indicating a goal is needed. Furthermore, we would like to enhance our search result by using learning algorithms.  

While looking for goals in football match reports, we are omitting the detection of team that scored as well as the unique recognition of a goal as many reports refer multiple times to the same goal.



Jochen. Einleitung, Uebertragbarkeit auf andere Text Mining Tasks. Steps to goal

\section{Structure and size of the data set}
Matze. siehe outline, punkt 1.2 Struktur input und struktur fuer web mining (satzweise getrennt)

\section{Preprocessing}
Matze: Wie wurde struktur aus vorherigem Abschnitt erreicht? 
Jochen: Gate

\section{Actual Web Mining}
Matze. Verbindung zur Vorlesung. Web mining techniken. Rapidminer prozess. classifier. Suche nach perfect settings. apply model 

\section{Evaluation}
Jochen. Resultate von Precision und Recall der Classification. Diskussion. Positive und negative Einflüsse auf ergebnisse. Analog fuer ungelabelte Daten 
\section{Conclusion}
Wrap-up.

\bibliographystyle{plain}
\bibliography{bibliography}
\end{document}
